\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-10-04 chapters/conclusion.tex
Update bttda formulation

\subsection{Investigated gaze-independence visual \acsp{bci}}

@@

@@

ITR, comfort and user satisfaction in on-line operation is the ultimate goal

also do advance calculations of what the information transfer rate would be
given reasonable accuracy, so that you can go in with a reasonable interface
that has state-of-the-art ITR

@@

%Have attention for the emotional impact

\subsection{Linear decoding methods}

>>>>

\subsection{Investigated gaze-independence visual \acp{bci}}

@@

\subsection{Decoding: keep it linear}

keep it linear
use linear methods, but impose specific structure on them reflecting properties
of the signal, either to make them better regularized or more robust to some
types of variation

\subsection{Working \emph{with} individuals \acs{sspi}}

@@

ITR in on-line operation is the ultimate goal
, and, ultimately, user satisfaction, which depends on performance, comfort and perception
also do advance calculations of what the information transfer rate would be
given reasonable accuracy, so that you can go in with a reasonable interface
that has state-of-the-art ITR

@@

Have attention for the personal aspect
